Title Goes Here

### 2024-02-09 analysis/paper/paper.qmd
minor edits and comments

year_ad_posted <- 
jobdata %>% 
  pull(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page) %>% 
  str_extract(.,  "[[0-9]]{4}-[[0-9]]{4}")

jobdata <- 
  jobdata %>% 
  mutate(year_ad_posted = year_ad_posted) %>% 
  drop_na()

@@

# starts at 2010-2011

@@

integer_breaks <- function(n = 5, ...) {
  fxn <- function(x) {
    breaks <- floor(pretty(x, n, ...))
    names(breaks) <- attr(breaks, "labels")
    breaks
  }
  return(fxn)
}

>>>>

year_ad_posted <- 
jobdata %>% 
  pull(url_to_data_source_e_g_paste_in_url_to_the_jobs_wiki_page) %>% 
  str_extract(.,  "[[0-9]]{4}-[[0-9]]{4}")
 # fix for 2021-22 and 2023

jobdata <- 
  jobdata %>% 
  mutate(year_ad_posted = year_ad_posted) %>% 
  drop_na(year_ad_posted)

@@

# starts at 2010-2011
# fix for 2021-22

@@
